### 2024-11-09 conteudo/introduction/intro.tex
Removing research questions

According to our studies and observations, the code duplication problem
outlined in the section above cannot be resolved by the solutions presented in
the formal or gray literature. To address this gap, we propose an approach to
identify and mitigate code duplications in the Linux kernel. Specifically, we
aim to develop a tool capable of detecting duplicated functions within the
kernel and establish strategies for mitigating these duplications.

In this research, we expect to extract patterns of software engineering
techniques, such as refactoring methods commonly used to mitigate code
duplications. These patterns will guide future contributors in tackling the
code duplication problem in the given context. To properly investigate our
proposed approach, we developed the following primary research question to
guide our study:

\textbf{RQ1:} What are effective approaches for identifying duplicate code in the
Linux kernel?

Given the complexity of the primary question, we formulated a supplementary
research question to assess midway results related to the performance of our
proposed tool in the Linux kernel. The supplementary research question is
defined as follows:

\textbf{RQ1.1:} How accurately does an approach detect duplicated functions
within the Linux kernel?

We adopt a multi-method research design utilizing various methodologies
throughout the study to address our research questions. We structured this work
into two phases, each employing distinct research methods.

In \textbf{Phase I}, we will propose, develop, and validate a tool capable of
identifying code duplications at the function level for the C programming
language. We expect this tool to effectively identify code duplications in the
Linux kernel, as our preliminary investigation suggests that code files in the
kernel often contain a mix of duplicated and non-duplicated functions. To
validate the tool, we will perform a triangulation of results by evaluating our
tool against code duplication databases used in the formal literature and by
conducting an empirical analysis on a randomly selected set of code files from
the AMD Display driver, which our tool identifies as containing duplications.
Chapter \ref{cha:method} provides a detailed explanation of our validation
process.

@@

Upon completing the first phase, we will have a validated tool for identifying
code duplications within the Linux kernel context. We can then proceed to the
second phase of our research, which focuses on mitigating these duplications.
In \textbf{Phase II}, we aim to discover practical strategies to address the
code duplications detected in the Linux kernel. To achieve this objective, we
have designed an ethnographic approach that allows us to interact with the
Linux community and collect artifacts that validate or refute our proposed
mitigation strategies.

Figure \ref{fig:reDesign} summarizes the research steps proposed in this work.

>>>>

Our studies and observations reveal that the code duplication problem described
in the previous section cannot be fully addressed by existing tools in
either the formal or gray literature. To fill this gap, we propose an approach
to identify and mitigate code duplications specifically within the Linux
kernel. Our approach includes the development of a tool capable of detecting
duplicated functions within the kernel and establishing strategies for
addressing these duplications.

@@

This research aims to identify patterns of software engineering techniques,
such as refactoring methods commonly used to address code duplications. These
patterns will serve as a guide for future contributors in mitigating code
duplication issues within this context. To investigate our approach, we use the
initial version of our tool to identify duplicate code in the Linux kernel,
specifically targeting parts of the AMD Display driver code. We will then
refactor portions of this code and submit patches to maintainers, providing
evidence of the tool's accuracy in detecting duplicate functions.

Our research design follows a multi-method approach, utilizing various
methodologies to answer our research questions. We have structured the study
into two phases, each employing different research methods.

In \textbf{Phase I}, we propose, develop, and validate a tool capable of
identifying code duplications at the function level within C codebases. We
expect this tool to effectively detect code duplications in the Linux kernel,
as preliminary investigations suggest that kernel code files often contain a
mix of duplicated and unique functions. To validate the tool, we will use a
triangulation method, comparing its results with established code duplication
databases referenced in the literature, and conducting an empirical analysis on
a randomly selected set of files from the AMD Display driver, which our tool
flags as containing duplications. A detailed explanation of our validation
process is provided in Chapter \ref{cha:method}.

Upon completing the first phase, we anticipate having a validated tool for
identifying code duplications within the Linux kernel context. We will then
proceed to the second phase, which focuses on strategies for mitigating these
duplications. In \textbf{Phase II}, our objective is to identify practical
approaches to address the code duplications detected in the Linux kernel. To
achieve this, we have designed an ethnographic approach that enables us to
interact with the Linux development community and gather artifacts that either
support or challenge our proposed mitigation strategies. Figure
\ref{fig:reDesign} summarizes the research steps proposed in this study.
